\Title

### 2020-01-23 manuscript/manuscript.tex
Describe EQL implementation in Harmonica

>>>>

\subsection{Equivalent sources implementation}

The subsequent comparisons between strategies for interpolating data through
equivalent sources are carried out by the equivalent sources implementation in
Harmonica \citep{harmonica}.

It solves equation~\ref{eq:linear-problem} by a least-squares fit, with
the option of adding a zeroth-order Tikhonov \citep{tikhonov} regularization
through a dimensionless \emph{damping} parameter.
This is achieved by scaling the Jacobian matrix so each column has unit
variance.

Define a diagonal matrix $S$, whose elements corresponds to the standard
deviation of each column of the Jacobian matrix $\mathbf{A}$:

\begin{equation}
    \mathbf{S} =
    \begin{bmatrix}
        \sigma_1 & \cdots &0 \\
        \vdots & \ddots & \vdots \\
        0 & \cdots & \sigma_M
    \end{bmatrix}.
\end{equation}

Equation~\ref{eq:linear-problem} can be written as:

\begin{equation}
    V(\mathbf{p})
    =
    \mathbf{A} \mathbf{S}^{-1} \mathbf{S} \mathbf{c}
    =
    \left[
        \mathbf{A} \mathbf{S}^{-1}
    \right]
    \left[
        \mathbf{S} \mathbf{c}
    \right]
    =
    \mathbf{A}' \mathbf{c}'
\end{equation}

\noindent where $\mathbf{A}'$ the scaled Jacobian matrix and $\mathbf{c}'$ is
a vector containing scaled coefficients.

Now we can define the misfit function as the sum between the data misift and
the Tikhonov regularization function:

\begin{equation}
    \phi(\mathbf{c'}) =
        \left\lVert V(\mathbf{p}) - \mathbf{A}'\mathbf{c}' \right\rVert ^ 2
        + \lambda \left\lVert \mathbf{c}' \right\rVert ^2,
    \label{eq:misfit}
\end{equation}

\noindent where $\lambda$ is a dimensionless damping parameter.

After solving the least squares problem, we obtain the set of scaled
coefficients $\mathbf{c}'$ that minimizes equation~\ref{eq:misfit}.
We can get the corresponding coefficients $\mathbf{c}$ by rescaling
$\mathbf{c}'$:

\begin{equation}
    \mathbf{c} = \mathbf{S}^{-1} \mathbf{c}'.
\end{equation}
